Modelling last glacial cycle ice dynamics in the Alps

### 2018-08-18 articles/cycle/alps-cycle.tex
Update data availability statement. DOIs pending.

\codedataavailability{%
    PISM is available as open-source software at http://pism-docs.org/.
    Aggregated model output will be made available upon publication. Please
    contact the corresponding author for more detailed model output data.}

>>>>

\codedataavailability{%
    PISM is available as open-source software at http://pism-docs.org.
    Aggregated model variables including those used to draw figures in this
    manuscript are available as geotiff (DOI application pending). Selected
    model output is available as compressed netCDF (DOI application pending).
    The supplementary animation can be found at \doi{10.5446/35164}.}
